Personality and political beliefs across the lifespan

### 2019-11-19 scripts/manuscript.Rmd
tidying (pivot_longer)

#Aggregating the social and economic conservationism scale (SECs)
items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12" )

@@

#Aggregating big 5 traits (TIPI)
items <- c("Q4_1", "Q4_2", "Q4_3", "Q4_4", "Q4_5", "Q4_6", "Q4_7", "Q4_8", "Q4_9", "Q4_10")

@@

```{r select}
#selecting the variables that we want to use
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize()
```

>>>>

#Aggregating the social and economic conservationism scale (SECs) using scoreItems from the psych package and mutate from dplyr
items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12" )

@@

#Aggregating big 5 traits (TIPI) using scoreItems from the psych package and mutate from dplyr
items <- c("Q4_1", "Q4_2", "Q4_3", "Q4_4", "Q4_5", "Q4_6", "Q4_7", "Q4_8", "Q4_9", "Q4_10")

@@

```{r select}
#selecting the variables that we want to use, cleaning, and characterizing dataset
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize()
```

```{r tidying}
#last step is to tidy our data
tidy <- data %>% 
  pivot_longer(cols = c(sec_economic_conservatism, sec_social_conservatism),
               names_to = "conservatism_type",
               names_prefix = "sec_",
               values_to = "conservatism_score") %>% 
  pivot_longer(cols = agreeableness:emotional_stability,
               names_to = "personality_trait",
               values_to = "personality_score")
```
